\subsection{Box 5: Managing large files}

Many biological applications require handling large data files.
While Git is best-suited for collaboratively writing small text files, nonetheless collaboratively working on projects in the biological sciences necesitates managing this data.

The example analysis pipeline in this tutorial starts by downloading data files in bam format which contain the alignments of short reads from a ChIP-seq experiment to the human genome.
Since these large, binary files are not going to change, there is no reason to version them with Git.
Thus hosting them on a remote http (as ENCODE has done in this case) or ftp site allows each collaborator to download it to her machine as needed, e.g. using \verb|wget|, \verb|curl|, or \verb|rsync|.
If the data files for your project are smaller, you could also share them via services like Dropbox or Google Drive.

However, some intermediate data files may change over time, and the practical necessity to ensure all collaborators are using the same data set may override the advice to \textit{not} put code output under version control, as described in Box 4.
Again returning to the ChIP-seq example, the first step calling the peaks is the most difficult computationally because it requires access to a Unix-like environment and sufficient computational resources.
Thus for collaborators that want to experiment with \verb|clean.py| and \verb|analyze.R| without having to run \verb|process.sh|, you could version the data files containing the ChIP-seq peaks (which are in bed format).
But since these files are larger than that typically used with Git, you can instead use one of the solutions for versioning large files within a Git repository without actually saving the file with Git, e.g. git-annex (\href{https://git-annex.branchable.com/}{git-annex.branchable.com}) or git-fat (\href{https://github.com/jedbrown/git-fat/}{github.com/jedbrown/git-fat}).
Recently GitHub has created their own solution for managing large files called Git Large File Storage (LFS) (\href{https://git-lfs.github.com/}{git-lfs.github.com}).
Instead of committing the entire large file to Git, which quickly becomes unmanageable, it commits a text pointer.
This text pointer refers to a specific file saved on a remote GitHub server.
Thus when you clone a repository, it only downloads the latest version of the large file.
And if you checkout an older version of the repository, it automatically downloads the old version of the large file from the remote server.
After installing Git LFS, you can manage all the bed files with one command: \verb|git lfs track "*.bed"|.
Then you can commit the bed files just like your scripts, and they will automatically be handled with Git LFS.
Now if you were to change the parameters of the peak calling algorithm and re-run \verb|process.sh|, you could commit the updated bed files and your collaborators could pull the new versions of the files directly to their local Git repositories.
