\textbf{Outline}

\begin{enumerate}
  \item Introduction to version control
  \begin{itemize}
    \item What is the problem?
    \begin{itemize}
      \item Filesystem full of analysis\_01, analysis\_02, analysis\_03\_final, etc.
      \item Collaborating via email. How to merge the changes made by different authors?
    \end{itemize}
    \item What is the solution? Explain basic idea of version control software
    \begin{itemize}
      \item Able to revert to past versions.
      \item Able to merge changes made asynchronously by multiple collaborators.
    \end{itemize}
    \item Why is it so powerful? Increased reproducibility and collaboration, not only for code but also manuscripts \cite{23448176}
\end{itemize}
  \item Using version control to track your code (as a single contributor)
  \begin{itemize}
    \item How to set up a repository
    \item How to tell version control what to commit
    \item How to commit new material and changes
    \item How to compare to old versions
    \item How to revert to previous versions
    \item \textbf{Figure 1} - Diagram "git add" and "git commit" steps
  \end{itemize}
  \item Using version control online (trying to avoid using jargon like "remote", which I realize I have jargon all over the place other than this one line, but we should think of how we should present the jargon to a biology audience probably)
  \begin{itemize}
    \item How to set up and link a remote repository to local repository
    \item Sync local and online versions of repositories
    \item \textbf{Figure 2} - Diagram "git push" and "git pull" steps with a remote repository
  \end{itemize}
  \item Using version control with collaborators
    \begin{itemize}
      \item Fork a repository
      \item Submit a pull request
      \item Fix merge conflicts
      \item \textbf{Figure 3} - Diagram collaboration using fork and pull request
  \end{itemize}
\end{enumerate}



\textbf{Potential box (or table) ideas:}
\begin{enumerate}
  \item Vocabulary: define things like commit, merge, branch, repo, etc...
  \item Other version control systems and hosting sites
  \item Branches (briefly introduce concept)
  \item What \textbf{not} to version control? Large, static data files; binary files like Word
\end{enumerate}